Measuring Political Freedom Around the World

### 2020-11-11 slides.Rmd
.

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE)
```

@@

---
# Best Subsets
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(adj.r.squared == max(adj.r.squared)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  rename(a_rsq = adj.r.squared) %>% 
  select(df, a_rsq, model) %>% 
  arrange(desc(a_rsq)) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3))
```
---
# Best Subsets
```{r, message=FALSE, warning=FALSE}
r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
  labs(title = "Best Subsets", x = "Parameters", y = "Adjusted R Squared") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_light(base_size = 12)
```

@@

```{r}
broom::tidy(model_df5) %>% 
  kableExtra::kable()
```
---
class: center
$$
\tiny
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kableExtra::kable() %>% 
  kableExtra::row_spec(4, bold = T, color = "white", background = "#D7261E")
```

@@

>>>>

```{r setup, include=FALSE}
source(here::here("R", "regression.R"))
library(kableExtra)
options(htmltools.dir.version = FALSE, echo = FALSE)
knitr::opts_chunk$set(echo = FALSE)
```

@@

---
# Best Subsets
```{r message=FALSE}
subsets %>% 
  group_by(df) %>% 
  filter(adj.r.squared == max(adj.r.squared)) %>% 
  mutate_if(is.numeric, round, 3) %>% 
  rename(a_rsq = adj.r.squared) %>% 
  select(df, a_rsq, model) %>% 
  arrange(desc(a_rsq)) %>% 
DT::datatable(fillContainer = FALSE, options = list(pageLength = 3))
```
---

class: center
### Best Subsets
```{r, message=FALSE, warning=FALSE, fig.align='center', fig.width=12, fig.height=8}
r <- subsets %>% group_by(df) %>% summarise(adj = max(adj.r.squared, na.rm = T))

subsets %>% 
  ggplot(aes(x = df, y = adj.r.squared)) + 
  geom_point() + 
  geom_smooth(data = r, aes(df, adj), se = FALSE, span = 0.5, color = "Green") + 
  labs(title = "", x = "Parameters", y = "Adjusted R Squared") + 
  scale_x_continuous(breaks = 1:9) + 
  theme_light(base_size = 30)

```

@@

```{r}
broom::tidy(model_df5) %>% 
  kable()
```
---
class: animated, fadeIn, center
$$
\tiny
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kable() %>% 
  row_spec(4, bold = T, color = "white", background = "#D7261E")
```

@@

class: center, top
<font size="1">
```{r results='asis',out.width='25%', fig.align='center'}
stargazer::stargazer(fit_df6, model_df5, fit_df4, type = "html", 
                     title = "Regression Results", 
                     covariate.labels = c(),header = FALSE,
single.row=FALSE,column.sep.width = "-15pt", column.separate = 1)
```

---
class: center, middle
